### 2015-08-16 doc/article/article.tex
removed reduction to compact location problem, was wrong

Given $n$ sets of $ m_1, m_2... m_n$ objects, the consensus problem is to find a set of $n$ objects, one per set, minimizing the sum of their pairwise distance.

>>>>

Given $k$ sets of $ m_1, m_2... m_n$ objects, the consensus problem is to find a set of $k$ objects, one per set, minimizing the sum of their pairwise distance. This is modelled as finding the smallest cycle in a complete $k$-partite graph.

% http://stackoverflow.com/questions/17168049/max-weight-k-clique-in-a-complete-k-partite-graph
% http://cstheory.stackexchange.com/questions/30679/k-clique-in-k-partite-graph
% http://cstheory.stackexchange.com/questions/30605/many-one-reduction-from-inequality-problem-to-equality-problem
\noindent The consensus problem is reformulated as the problem of finding a minimal $k$-clique in a complete weighted $k$-partite graph where $k$ is a free parameter. This problem is known to be intractable
